### 2016-01-28 results.Rmd
ENH:  more.

@@

>>>>

<!--

* Evaluation
    * Proper context
        * We only have manual labelings from a single radiologist (
        * TBI white matter hyperintensities are more difficult to segment than MS lesions
            * individual lesions are smaller
            * lesion load is typically smaller
            * not prone to enhancement
            * less distinct from surrounding tissue ?
    * Despite the doubts regarding the efficacy of a typical segmentation validation,
      our contribution is useful because
         * the total segmentation framework is publicly available within the ANTs/ANTsR
           framework
         * although only a single site is analyzed, the feature images are site-agnostic
              * we plan to apply the current RF models directly to the other site data
              * we can then build the training database further by enlisting other experts
         * Is this the first work exploring segmentation of white matter hyperintensities in TBI?
         * The data (including manual tracings) will be made available as part of the FITBIR
           effort.

-->

@@

As mentioned previously, segmentation of white matter hyperintensities in traumatic brain
injury cohorts is a much more difficult problem than
